---
title: "An Analysis of a Survey on Masculinity"
author: "Natascha Otto"
date: "1 11 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# this is where you could also disable the message outputs from some of the below chunks
```


```{r, echo=FALSE}
# TODO maybe write these nice descriptions in the text so that readers can read them? 
# they seem pretty close to a writeup of the analysis.
# In this chunk I selected and cleaned up certain variables from the raw data set
# and proceeded to create a new data frame to work with.
# technically as per http://style.tidyverse.org there should be a single space after 3

# these library calls are causing some spurious output; you might want to place these calls in the above chunk and then silence that chunk
library(dplyr)
raw_data <- readr::read_csv(file = "data/raw_responses.csv")
library(tidyr)
library(forcats)

data <- raw_data %>%
  select(q0002, q0021_0001, q0021_0002, q0021_0003, q0021_0004, q0024, age3) %>%
  rename(
    mascImportance = q0002, 
    sexBoundaries_tooFar = q0021_0001, 
    sexBoundaries_talkFriend = q0021_0002, 
    sexBoundaries_talkEx = q0021_0003, 
    sexBoundaries_none = q0021_0004, 
    marriageStatus = q0024, 
    age = age3
  ) %>% 
  mutate(
    sexBoundaries_tooFar = sexBoundaries_tooFar != "Not selected",
    sexBoundaries_talkFriend = sexBoundaries_talkFriend != "Not selected",
    sexBoundaries_talkEx = sexBoundaries_talkEx != "Not selected",
    sexBoundaries_none = sexBoundaries_none != "Not selected",
  ) %>%
  mutate(
    mascImportance = ordered(
      x = mascImportance, 
      levels = c("Very important", "Somewhat important", "Not too important", "Not at all important", "No answer")
    ),
    age = ordered(
      x = age,
      levels = c("18 - 34", "35 - 64", "65 and up")
    )
  )
```


## The importance of being seen as masculine
### This part conveys how important it is to men to be seen as masculine in form of a bar chart.

```{r}
#This chunk conveys how important it is to men to be seen as masculine in form 
#of a bar chart.

## Plot
library(ggplot2)
ggplot(
  data = data, 
  mapping = aes(x = mascImportance, fill = mascImportance)
) + 
  geom_bar(alpha = 0.5)
```


## Age and the importance of being seen as masculine 
### This part depicts the correlation between age and the importance of being seen as masculine via a crosstable and a plot.

```{r}
#This chunk depicts the correlation between age and the importance of being 
#seen as masculine via a crosstable and a plot.

## Crosstable 
importanceAge <- with(data, table(age, mascImportance))
importanceAge <- round(addmargins(prop.table(importanceAge)*100), 2)

##  Plot
ggplot(
  data = data,
  mapping = aes(x = age, y = mascImportance, colour = mascImportance)
) + 
  geom_count(alpha = 0.5) 
```


## How sexual boundaries were gauged in the last 12 months 
#### This part shows how men estimated whether they pushed a partner too far in a past sexual encounter

```{r}
#This chunk deals with the question how the interviewed men gauged sexual boundaries
#in the last 12 months. To guarantee an easier work flow and because the question 
#was designed to have the option of multiple choice answers and was therefore depicted
#with a variable for each question, I decided to select the relevant variables and
#combine them in a smaller data frame dedicaded to the topic of sexual boundaries. 
#Later on I also decided to recode each variable into factors for nicer plots.

library(tidyr)
sexBoundaries <- raw_data %>%
  select(q0021_0001, q0021_0002, q0021_0003, q0021_0004) %>%
  rename(
    sexBoundaries_tooFar = q0021_0001, 
    sexBoundaries_talkFriend = q0021_0002, 
    sexBoundaries_talkEx = q0021_0003, 
    sexBoundaries_none = q0021_0004) 

sexBoundaries$sexBoundaries_tooFar <- factor(
  sexBoundaries$sexBoundaries_tooFar, 
  levels = c(
    "Wondered whether you pushed a partner too far in a past sexual encounter.", 
    "Not selected"
  ), 
  labels = c("yes", "no")
)

sexBoundaries$sexBoundaries_talkFriend <- factor(
  sexBoundaries$sexBoundaries_talkFriend, 
  levels = c(
    "Talked with a friend or friends about whether you pushed a partner too far.", 
    "Not selected"
  ), 
  labels = c("yes", "no")
)

sexBoundaries$sexBoundaries_talkEx <- factor(
  sexBoundaries$sexBoundaries_talkEx, 
  levels = c(
    "Contacted a past sexual partner to ask whether you went too far in any of you sexual encounters.",
    "Not selected"
  ), 
  labels = c("yes", "no")
)

sexBoundaries$sexBoundaries_none <- factor(
  sexBoundaries$sexBoundaries_none, 
  levels = c("None of the above", "Not selected"), 
  labels = c("yes", "no")
)
```

### Plot for those who wondered whether they pushed a partner too far in a past sexual encounter

```{r}
ggplot(
  data = sexBoundaries,
  mapping = aes(sexBoundaries_tooFar, fill = sexBoundaries_tooFar)
) + 
  geom_bar(alpha = 0.5)
```

### Plot for those who talked to friends about whether they pushed a partner too far

```{r}
ggplot(
  data = sexBoundaries,
  mapping = aes(sexBoundaries_talkFriend, fill = sexBoundaries_talkFriend)
) + 
  geom_bar(alpha = 0.5)
```

### Plot for those who talked to an Ex about whether they pushed a partner too far

```{r}
ggplot(
  data = sexBoundaries,
  mapping = aes(sexBoundaries_talkEx, fill = sexBoundaries_talkEx)
) + 
  geom_bar(alpha = 0.5)
```

### Plot for those who didn't do any of the above

```{r}
ggplot(
  data = sexBoundaries, 
  mapping = aes(sexBoundaries_none, fill = sexBoundaries_none)
) + 
  geom_bar(alpha = 0.5)
```

